---
title: "ONT Native Barcoding 96 V14"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)

```


This protocol is for Oxford Nanopore sequencing using ligation with the SQK-NBD114.96 kit (revO 15Sep2022).  

***

**1. DNA repair and end-prep (Opentrons)**  

 - In a 96-well plate, add 400 ng DNA per sample
 - Make up to 12 ul with water
 - Prepare ER master mix:
 
```{r table1, results='asis'} 

kbl(
  data.frame(
    . = c('NEBNext FFPE DNA Repair Buffer', 'Ultra II End-prep Reaction Buffer', 'Ultra II End-prep Enzyme Mix', 'NEBNext FFPE DNA Repair Mix'),
    vol = c('0.875 ul', '0.875 ul', '0.75 ul', '0.5 ul')
  )
) %>%
  kable_styling(position = 'left', full_width = F, bootstrap_options = 'hover', 'condensed') %>%
  row_spec(0, bold = F, background = '#999999;', color =  '#fff;')
```

 - Add 3 ul ER master mix to each sample, mix thoroughly
 - incubate 20 degrees for 5 minutes
 - incubate 65 degrees for 5 minutes

*** 
 
**2. Native barcode ligation and pooling (Opentrons)**  

 - Thaw reagents at RT
 - In a **new** 96-well plate, add the following:
 
```{r table2, results='asis'} 

kbl(
  data.frame(
    . = c('water', 'End-prepped DNA', 'Native Barcode (NB0-96)', 'Blunt/TA Ligase Master Mix'),
    vol = c('3 ul', '0.75 ul', '1.25 ul', '5 ul')
  )
) %>%
  kable_styling(position = 'left', full_width = F, bootstrap_options = 'hover', 'condensed') %>%
  row_spec(0, bold = F, background = '#999999;', color =  '#fff;')
```
 
 - Mix thoroughly
 - Incubate 20 min RT
 - Add 2 ul EDTA
 - Pool the barcoded samples in a clean tube
 
***

**3. Continue protocol with pool (manual pipetting)**



