---
title: ""
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)

```


This protocol is for Oxford Nanopore sequencing of plasmid or bacterial genome samples using the rapid barcoding kit (SQK-RBK114.96).  

**1. Tagmentation**  

 - adjust DNA with water, add barcodes (Opentrons). For gDNA, use 50 ng/sample if > 4 samples and 200 ng/sample if < 4 samples.
```{r table1, results='asis'} 

kbl(
  data.frame(
    . = c('DNA + water', 'rapid barcode', 'total'),
    gDNA = c('10.0 ul', '1.0 ul', '11 ul'),
    plasmid = c('5.0 ul', '0.5 ul', '5.5 ul')
  )
) %>%
  kable_styling(position = 'left', full_width = F, bootstrap_options = 'hover', 'condensed') %>%
  row_spec(3, bold = T)

```

 - incubate 30 degrees for 2 minutes
 - incubate 80 degress for 2 minutes

*** 
 
**2. Pool and purify**  

 - pool all samples (Opentrons), note down volume  
 - add equal volume SPRI beads, incubate 5 min room temperature  
 - wash beads 2x with 80% EtOH  
 - aspirate all EtOH and dry beads 30 seconds  
 - resuspend in 15 ul EB, incubate 10 minutes, take out eluate in new tube (increase the elution volume by 15ul for each 12 plasmids in the pool)  
 
***

**3. RAP addition**  

 - measure pool conc with Qbit  
 - use 50 fmol in 5 ul (Flongle) or 100 fmol in 11 ul (MinION)
 - dilute adaptor - 1.5 ul rapid adapter (RA) + 3.5 ul adapter dilution buffer (ADB)
 - add diluted adaptor 0.5 ul (Flongle) or 1 ul (MinION)
 - incubate 5 min RT
 - put on ice

***

**4. Load flow cell - use max 20 fmol for R10.4.1**  

 - prime flow cell - 30 ul FCT + 5 ul BSA at 50 mg/ul to one vial (1170 ul) of FCF (MinION)
 - library mix

```{r table2, results='asis'} 
kbl(
  data.frame(
    . = c('Sequencing buffer (SB)', 'Library beads (LIB)', 'Library', 'Total'),
    Flongle = c(15, 10, 5, 30),
    MinION = c(37.5, 25.5, 12.0, 75.0)
  )
) %>%
  kable_styling(position = 'left', full_width = F, bootstrap_options = 'hover', 'condensed') %>%
  row_spec(4, bold = T)
  #kable_styling(full_width = F, position = "left")
  

```


Load 2 or more times if needed and enough library is present

***

**5. Data analysis**   

Use high accuracy basecallig and demultiplexing in MinKNOW. Recommended pipelines:   
<a href="https://github.com/epi2me-labs/wf-clone-validation" target="_blank">plasmid de novo assembly pipeline</a>   
<a href="https://github.com/epi2me-labs/wf-bacterial-genomes" target="_blank">bacterial genomes pipeline</a>



